### 2017-04-01 manuscript/publication-si-recipe.tex
Final review of supporting information

\section{LCIA Case Study: Marine Eutrophication}

@@

Briefly, the implementations correspond on many significant flows but differ on several as well.
\begin{itemize}
\item While all methods characterize ammonia to air and ammonium ion to water, only ILCD characterizes ammonia to water and ammonium to air.
\item Where Ecoinvent characterizes ``nitrogen oxides'', ILCD separately characterizes nitrogen dioxide and nitrogen monoxide.  Since neither are present in the Ecoinvent data sets, the ILCD method will miss these flows entirely.
\item Ecoinvent includes characterizations for two different forms of elemental nitrogen, but ILCD is characterized with respect to a third flow, which is likely a synonym.  As a consequence, the ILCD implementation will not capture elemental nitrogen emissions from Ecoinvent datasets.
\item Cyanide emissions are only included in ``without long-term'', and do not appear in the ``long-term'' emissions nor in ILCD.
\item Nitrite is omitted from the ``long-term'' characterization but included in ``without long-term.''
\item The characterization for nitrogen oxides in ``without long-term'' is a factor of 10 smaller than it is in ``long term.''
\end{itemize}
This example demonstrates how independent reimplementation of LCIA methods can produce inaccurate and/or inconsistent results.

\begin{table}
  \footnotesize\sffamily
  \caption{ReCiPe Marine Eutrophication, Midpoint, kg N-equivalent}
  \input{lcia_table}
\end{table}

>>>>

\
\section{LCIA Case Study: Marine Eutrophication}
\renewcommand{\bottomfraction}{.8}
\begin{table}[b]
  \footnotesize\sffamily
  \caption{ReCiPe Marine Eutrophication, Midpoint, kg N-equivalent}
  \label{table:recipe}
  \input{lcia_table}
\end{table}

@@

Briefly, the implementations correspond on many significant flows but differ on several as well.
\begin{itemize}
\item While all methods characterize ammonia to air and ammonium ion to water, only ILCD characterizes ammonia to water and ammonium to air.
\item Where Ecoinvent characterizes ``nitrogen oxides'', ILCD separately characterizes nitrogen dioxide and nitrogen monoxide.  Since neither are present in the Ecoinvent data sets, the ILCD method will miss these flows entirely.
\item Ecoinvent includes characterizations for two different forms of elemental nitrogen, but ILCD is characterized with respect to a third flow, which is likely a synonym.  As a consequence, the ILCD implementation will not capture elemental nitrogen emissions from Ecoinvent datasets.
\item Cyanide and nitrite emissions are only included in ``without long-term'', and do not appear in the ``long-term'' emissions.  Cyanide emissions do not appear at all in ILCD.
\item The characterization for nitrogen oxides in ``without long-term'' is a factor of 10 smaller than it is in ``long term.''
\end{itemize}
This example demonstrates how independent reimplementation of LCIA methods can produce inaccurate and/or inconsistent results.

### 2017-04-01 manuscript/publication-si-spreadsheet.tex
Final review of supporting information

Each entity type (aside from characterization quantities) has additional descriptive fields:
\begin{itemize}
\item The \emph{flow direction} describes the direction of each flow with respect to the entity being defined.  Foreground flows, background dependencies, cutoff flows and elementary flows all have directions.
\item Foreground nodes also have a \emph{flow name} that reports the name of the reference flow emanating from the node.
\item Background dependencies also have a \emph{reference flow} that tells which of the process's reference outputs is being used.  In the case of multi-output background processes, this field is necessary to identify the appropriate allocation result.
  \item Cutoff and elementary flows also have a \emph{compartment} that describes which environmental compartment the flow is exchanged with. For cutoff flows, the compartment may be used to document some kind of classification of the flow.
\end{itemize}
Note that cutoff flows and elementary flows are both included in the foreground emission matrix, $B_f$, because they are mathematically equivalent.  In other words, ``emissions'' can be interpreted to include any flows that are exterior to the technology matrix, including resource extraction, environmental releases, and cutoffs.

>>>>

Each entity type (aside from characterization quantities) has additional descriptive fields:
\begin{itemize}
\item The \emph{flow direction} describes the direction of each flow with respect to the entity being defined.  Foreground flows, background dependencies, cutoff flows and elementary flows all have directions.
\item Foreground nodes also have a \emph{flow name} that reports the name of the reference flow emanating from the node.
\item Background dependencies also have a \emph{reference flow} that tells which of the process's reference outputs is being used.  In the case of multi-output background processes, this field is necessary to identify the appropriate allocation result.
  \item Elementary flows also have a \emph{compartment} that describes which environmental compartment the flow is exchanged with. This is used to determine the correct characterization factor.
\end{itemize}
Note that cutoff flows and elementary flows are both included in the foreground emission matrix, $B_f$, because they are mathematically equivalent.  In other words, ``emissions'' can be interpreted to include any flows that are exterior to the technology matrix, including resource withdrawals, environmental releases, and cutoffs.
